Testing atlantisom: generate census length comps for Norwegian Barents Sea Atlantis

### 2019-05-13 visualization_Rmd/NOBATrueLengthCompTest.Rmd
change NOBA to annual output

@@

Here we use `create_survey` on the numbers output of `run_truth` to create the survey census of age composition.

@@

survey_testNall <- create_survey(dat = truth$nums,
                                 time = timeall,
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

@@

First we subset the nums, resn, and structn components of `run_truth` using the same `create_survey` design selecting boxes, time, and species. We need only apply survey efficiency and selectivity to nums, however (done above), so we apply `aggregateDensityData` here.

@@

# aggregate true resn per survey design
survey_aggresnall <- aggregateDensityData(dat = truth$resn,
                                 time = timeall,
                                 species = survspp,
                                 boxes = boxall)

# aggregate true structn per survey design
survey_aggstructnall <- aggregateDensityData(dat = truth$structn,
                                 time = timeall,
                                 species = survspp,
                                 boxes = boxall)

@@

This code block can take hours (5+ for CCA and 18+ for NOBA) to run, so be prepared, but then the saved file can be read back in to have length comps for all surveyed species. For a normal survey query we would have only one output timestep per year, which should save some time.

@@

```{r loadlengthcomp, echo=TRUE, eval=FALSE}

@@

```{r moreplots, echo=TRUE, eval=FALSE}

@@

So this looks like our best approximation of a true length comp for a particular Atlantis run. Comparisons with standard surveys next.

>>>>

# not enough memory to do all NOBA outputsteps, change to once per year
midptyr <- round(median(seq(1,stepperyr)))

annualmidyear <- seq(midptyr, noutsteps, stepperyr)

@@

Here we use `create_survey` on the numbers output of `run_truth` to create the survey census of age composition. *Sampling once per year, rather than output timestep.*

@@

survey_testNall <- create_survey(dat = truth$nums,
                                 time = annualmidyear,
                                 species = survspp,
                                 boxes = boxall,
                                 effic = effic1,
                                 selex = selex1)

@@

First we subset the nums, resn, and structn components of `run_truth` using the same `create_survey` design selecting boxes, time (*once per year for NOBA*), and species. We need only apply survey efficiency and selectivity to nums, however (done above), so we apply `aggregateDensityData` here.

@@

# aggregate true resn per survey design
survey_aggresnall <- aggregateDensityData(dat = truth$resn,
                                 time = annualmidyear,
                                 species = survspp,
                                 boxes = boxall)

# aggregate true structn per survey design
survey_aggstructnall <- aggregateDensityData(dat = truth$structn,
                                 time = annualmidyear,
                                 species = survspp,
                                 boxes = boxall)

@@

This code block can take hours (5+ for CCA and estimated 17+ for NOBA, but it never finished after 32+) to run, so be prepared, but then the saved file can be read back in to have length comps for all surveyed species. For a normal survey query we would have only one output timestep per year, which should save some time.

And lets change NOBA to estimate length only 1 timestep per year (~2.5 hours to run):

@@

```{r loadlengthcomp, echo=TRUE}

@@

```{r moreplots, echo=TRUE}

@@

So this looks like our best approximation of a true length comp for a particular Atlantis run (although it seems critical to limit output to allow functions to finish). Comparisons with standard surveys next.
